Investigating the influence of genre preferences on movie/series rating patterns

### 2024-03-23 gen/paper/paper.Rmd
added descriptives of the dataset to the paper

| Name of Variable | Contents of Variable                                                                                                                                             | Used as .. in Analysis |
|------------------|------------------------------------------------------------------------------------------------------------------------------------------------------------------|------------------------|
| Average Rating   | The average rating on IMBd per title of a given movie or series.                                                                                                 | Dependent Variable     |
| Genre Types      | Genre Types is a cluster for all 26 genre dummies that contain the value 1 if the movie or series contains that genre and otherwise 0.                           | Independent Variable   |
| titleType        | This variable indicates whether a title is a movie or a series.                                                                                                  | Fixed Effect           |
| Title            | The title is the given title of any unique movie or series                                                                                                       | Fixed Effect           |
| 5 Year Window    | The 5 year windown (or ' slide_window_5' indicates between what 5 year window a movie or series belongs to. For example a movie from 2003 belonging to 2000-2004 | Split Varible          |

@@

The average IMBd rating is used as the outcome variable for the
analysis. However, this average rating is influenced by the number of
votes that compile this average. This can be the case because each
rating, including the extreme ones, receives more weight when
calculating the average, simply because there are only a few ratings.
So, the average ratings may be more extreme, causing to skew the overall
results. Therefore, movies/series receiving a number of votes below the
cut-off of a hundred will not be included in the regression analysis.

>>>>

| Name of Variable | Contents of Variable                                                                                                                                             | Used as .. in Analysis |
|------------------|------------------------------------------------------------------------------------------------------------------------------------------------------------------|------------------------|
| Average Rating   | The average rating on IMDb per title of a given movie or series.                                                                                                 | Dependent Variable     |
| Genre Types      | Genre Types is a cluster for all 26 genre dummies that contain the value 1 if the movie or series contains that genre and otherwise 0.                           | Independent Variable   |
| titleType        | This variable indicates whether a title is a movie or a series.                                                                                                  | Fixed Effect           |
| Title            | The title is the given title of any unique movie or series                                                                                                       | Fixed Effect           |
| 5 Year Window    | The 5 year window (or ' slide_window_5' indicates between what 5 year window a movie or series belongs to. For example a movie from 2003 belonging to 2000-2004 | Split Variable          |

### Descriptives
The data set contains of 70087 films, of which 60246 are movies and 9841 are series.  These films have on average a rating of 6.3, with 10 being the highest and 1 being the lowest. After removing the votes to all being above 100, the average number of votes on a film became 7146. When looking at the years, the most amount of films were released on IMDb in 2019, with 2586 films. Also when comparing the 5 year range of films released,2015 to 2019 had the most films released, with 11353 films. Looking at the runtime of the films, on average a film is 101 minutes long.

@@

The average IMDb rating is used as the outcome variable for the
analysis. However, this average rating is influenced by the number of
votes that compile this average. This can be the case because each
rating, including the extreme ones, receives more weight when
calculating the average, simply because there are only a few ratings.
So, the average ratings may be more extreme, causing to skew the overall
results. Therefore, movies/series receiving a number of votes below the
cut-off of a hundred will not be included in the regression analysis.
